Investigating Cross-Sectional Size Distribution of Randomly Distributed 3D Spheres

### 2020-05-24 Paper/main.tex
Added all citations

If we compute the integral in Equation~\ref{eq:phi_OG}, replacing $f(R)$ with
$\delta(R-R_0)$ we find:
\begin{equation}
\phi(x) = \int_{x}^{\infty}\frac{x\delta(R-R_0)}{\sqrt{R^2 - x^2}} =
\frac{xH(R_0-x)}{\sqrt{R_0^2-x^2}}
\label{eq:phi_constant}
\end{equation}
where $H(R_0 - x)$ is the heaviside function, which ``turns on'' the
distribution only for $x < R0$ as it is not possible to have a circular radius
$x$ larger than the spherical radius. So we aim to see our experimental data
reproduce this distribution. We also investigated how changing the
value of $R_0$ affects the experimental distribution.

@@

Indeed, we found that making the sphere sizes much larger made the placing of
the spheres in a finite space more difficult, and exponentially increased the
time complexity of the placing algorithm. This is because if the placed spheres
are too large, while it is initially easy to place spheres, as more are placed,
more coordinates must be randomly drawn before one if found for the next sphere
to be placed into. It is also possible that the algorithm never finds a possible
coordinate for later spheres. One possible solution to this may be to use a
better placing algorithm. Choosing a tight packing algorithm %\cite{Chen2001} would
maximise the number of spheres of a given radius that can be placed. However,
this would likely result in a less than random distribution of spheres if the
spheres are all of identical sizes. This would likely cause some systematic
error in the data, and so it was not investigated here. If we randomised the
sizes of the spheres as we do in the next part of the investigation, the problem
become significantly more complicated. Tight packing algorithms for irregular
shaped objects are very difficult to create and computationally expensive
\todo{cite}.

@@

However, it would be more prudent to use a Gaussian distribution to draw the
values of the noise. This is because it is likely that the many sources of error
possible in an experimental measurement of particle cross-sections in a material
will be convoluted together into a Gaussian distribution of errors due to the
central limit theorem \cite{Islam2018}.

@@

\printbibliography{}
\end{document}

>>>>

If we compute the integral in Equation~\ref{eq:phi_OG}, replacing $f(R)$ with
$\delta(R-R_0)$ we find:
\begin{equation}
\phi(x) = \int_{x}^{\infty}\frac{x\delta(R-R_0)}{\sqrt{R^2 - x^2}} =
\frac{xH(R_0-x)}{\sqrt{R_0^2-x^2}}
\label{eq:phi_constant}
\end{equation}
where $H(R_0 - x)$ is the heaviside function, which ``turns on'' the
distribution only for $x < R0$ as it is not possible to have a circular radius
$x$ larger than the spherical radius. So we aim to see our experimental data
reproduce this distribution \cite{Kong2005}. We also investigated how changing the
value of $R_0$ affects the experimental distribution.

@@

Indeed, we found that making the sphere sizes much larger made the placing of
the spheres in a finite space more difficult, and exponentially increased the
time complexity of the placing algorithm. This is because if the placed spheres
are too large, while it is initially easy to place spheres, as more are placed,
more coordinates must be randomly drawn before one if found for the next sphere
to be placed into. It is also possible that the algorithm never finds a possible
coordinate for later spheres. One possible solution to this may be to use a
better placing algorithm. Choosing a tight packing algorithm \cite{Chen2001} would
maximise the number of spheres of a given radius that can be placed. However,
this would likely result in a less than random distribution of spheres if the
spheres are all of identical sizes. This would likely cause some systematic
error in the data, and so it was not investigated here. If we randomised the
sizes of the spheres as we do in the next part of the investigation, the problem
become significantly more complicated. Tight packing algorithms for irregular
shaped objects are very difficult to create and computationally expensive
\cite{Ma2018}.

@@

However, it would be more prudent to use a Gaussian distribution to draw the
values of the noise. This is because it is likely that the many sources of error
possible in an experimental measurement of particle cross-sections in a material
will be convoluted together into a Gaussian distribution of errors due to the
central limit theorem \cite{Islam2018}. Thus, it would be necessary for any
experimentalist attempting to carry out a similar investigation with real
materials, perhaps to determine porosity \cite{Lekakh}, to carefully consider
all errors in measurements.

@@

\printbibliography

\end{document}
